\section{Use of Gamification in \app{}}
\label{sec:useofgamificationinapp}

\subsection{Design Rationale for Gamification System in \app{}}
\label{sec:designrationalegamification}
In AsthmAPP we aimed to use gamification as a distraction and rewarding element for the children. During the start of the project we arranged a brain-storming session to find which gamification techniques we wished to add to \app{} and \ab{}. The summary of this session is listed in Chapter \ref{sec:combininggamemechanismsinasthmapp}. 

At first thought, we figured that implementing an avatar system was a smart approach to create a gamification system. An avatar system gives possibilities for expansion in order for the application to combat boredom in the long run. When developing avatar systems, a key for its success is that it is balanced and good looking. After having spent a few hours programming an avatar system, we chose to discard the functionality, caused by the lack of skills necessary to make it attractive. 

We chose to aim for a system we were sure we were able to implement in a well-working fashion in order to test the system with users. We expanded on Aaberg \etal{}'s use of experience points (represented by stars), by adding a shop where the stars may be used for purchasing rewards. We believed this system has many possibilites for expanding upon on a later stage. The parents have the possibility to create their personalized gamification environment through the reward system. This solution stands to reason with the arguments of Nicholson regarding how to design gamification\cite{nicholson2012user}.

The children are rewarded with stars based on their health state. The rationale behind this is that the children may have to take more medicine when they have a cold or there is a lot of pollen in the air. The parents have access to a administrator menu where they may add new rewards for the children. The children will then be able to order the rewards when they have earned a sufficient number of stars. This way the parents and the children create their own gamification environment. Examples of possible rewards could be to give the child an extra 10 NOK in weekly allowance, taking him/her to soccer matches or even to the local amusement park. It is an option where the only boundary is the imagination and how much cost and effort parents wish to invest in it.    

The rewards will appear on a ``milestone'' basis. We do not want children to feel that they lose something if they spend stars on a reward. We do not want to force parents into giving away rewards they cannot afford or do not wish to give. The use of the reward system is optional and decided by the user, making the user in control of how they wish to gamify the experience. 
We do not wish to have the children spending too much time using the application, since using a tablet or phone at such a young age is considered unhealthy. This had some implications on the complexity of our gamification system. 


\subsection{Gamification Elements in AsthmAPP}
\label{sec:combininggamemechanismsinasthmapp}

We did an assesment of the different gamification elements in order to decide which gamification element suited our purpose. This assesment is included in Table \ref{tab:game-mech-in-astmapp}. 

\begin{onehalfspacing}
\begin{table}[H]
\begin{tabular}{| p{2.5cm} | p{2.1cm} | p{8.8cm} | }
	\hline
	\textbf{Mechanism} & \textbf{Included in AsthmAPP} & \textbf{Rationale} \\
	\hline
	Avatar systems & No & We did not have time to implement this during our thesis, but we do believe this could be a good feature if it was implemented in a right manner.    
	 \\
	\hline
	Achievements and badges & No & We believe our target group will not enjoy this feature as much as older children, e.g. those of 12 - 16 years of age.  \\
	\hline 
	Real-world rewards & Yes & Children enjoy the feeling of being rewarded with something real.
	 \\
	\hline
	Mirroring user behavior & Yes & Demonstration has a positive effect on children.
	\\
	\hline
	Leaderboards & No & There are no way to implement this in a realistic and legal way. Children would have to share their data, which consists of points based on medicine doses. Parents could be blamed if their child were on the bottom of the list. It would also be negative for small children's motivation if their effort is not reflected on the leaderboard. 
	\\
	\hline
	Social networking & No & Much of the same reasons as why we did not choose leaderboards. We also believe that children in our target group would not understand this aspect.  
	\\
	\hline
	Progress bar & No & In an ideal world, we could have shown how close the child was to becoming fully treated for asthma. However, identifying how close a patient is to becoming healthy, is virtually impossible. Another usage may be to match the child's progress for each week against his/her medicine plan. This would however, imply that by-need treatments would not be included, which may seem unfair for the child. Additionally, their progress would be deleted every week, which would not have much motivational effect.  
	\\
	\hline
	Experience points & Yes & The stars will work as experience points, which may used to cash in rewards from the parents. 
	\\
	\hline
	Contests & No & Using medical history to participate in contests would be a violation of Norwegian privacy laws. It may also be used to pinpoint ``bad'' parents.      
	\\
	\hline
\end{tabular}
\caption{Assessment of different game mechanisms}
\label{tab:game-mech-in-astmapp}
\end{table}
\end{onehalfspacing}

\subsection{Criticism of \app{}'s Gamification System}
Chapter \ref{chp:gamification} gave an introduction to the term gamification, and how gamification should be used. We have developed a reward system that is highly based on parents' opinions, and thus, have some flaws that we will discuss further in the following. 

First of all, children may become bored of the rewards if they are not increasingly difficult to achieve, and have not increased in value. For instance, if a child is rewarded with a ticket to a football match for achieving 10 stars, and then receives a piece of chewing gum if he/she achieves 20 stars, the child may lose interest and important motivation in order to complete his/her treatment. 

Secondly, the number of stars rewarded depends on the child's inferred health state (green state yields 1 star, orange state yields 3 stars and red state yields 5). This calculation of rewards leaves a possible exploit where children may pretend to be sicker than they are. In the long run, a child could fake being sicker than he/she actually is, just to achieve a reward more easily. This is a situation that \emph{could} occur, but we did not have the resources necessary to observe this pattern over time.

Thirdly, the gamification during the treatment, i.e. the animation on the phone, could become boring over time. 
The interactions are not varied, and it takes approximately 2 minutes to complete a treatment. For expert users, who have had asthma for several years, it will become boring. Thus it should be noted that this is an application that probably would work best for young children in the early stage of their disease.  
