\chapter{Introduction}
\label{introduction}

This chapter will give an introduction to the study. It will state the purpose, motivation, research questions and the research method for this study. 

\section{Purpose}
\label{purpose}
The purpose of this study is to evaluate the CAPP, GAPP and Karotz Applications created by Aaberg, Aarseth, Dale, Gisvold and Svalestuen [Insert reference].
The evaluation will be done through usability testing done on all three applications. The results of these inital tests will then be used to improve the applications for a newer version. 
We will also plan a thorough testing of the applications.


\section{motivation}
According to NAAF(``The Norwegian Asthma and Allergy Association'') 20\% of the Norwegian popularity has or have had asthma at the age of 10, and 8\% of the adult popularity suffer from asthma. Many of these children find it unpleasant to use their medicine, as they often don't understand why the medicine must be taken [Should have a reference]. This often results in parents applying the medication incorrectly, apply the wrong treatment, or even forget to give the medication to their children. 

BLABLABLA


\section{Research Questions}
\label{reseachquestions}
The main goal for this study is to evaluate the CAPP, GAPP and Karotz application, and identify the usability problems in these systems. Structuring the goals into different research questions will help this study with the evaluation of the goal. The goal has been composed into these questions:

\paragraph{RQ1:}
\textbf{Which Pokémon is really the coolest?}

\paragraph{RQ2:}
\textbf{What will I have for lunch today?}

This evaluation should be done through user testing and feedback from future users of the applications. The testing will give information on how well the 
\ldots

\section{Research Method}
\label{researchmethod}


