\chapter{Background}
\label{chp:background}


This chapter will give a brief introduction to the history behind the BLOPP project [insert reference] and the CAPP, GAPP and Karotz applications.


\section{BLOPP Project}
\label{sec:bloppproject}
Barns Legemiddelopplevelser is a project group ...

\subsection{CAPP/GAPP/Karotz project}
In the autumn of 2012 Aaberg, Aarseth, Dale, Gisvold and Svalestuen were engaged by the BLOPP Project group through the course ``TDT4290 - Customer Driven Project'' \cite{customerdrivenntnu} at NTNU. During period of August 2012 to December 2012 they developed a tangible medical reminder named CAPP/GAPP/KAPP. A full report of their work is available at [Insert Reference]. 
Their prototype is the foundation for our work in this project.


\section{CAPP/GAPP/KAPP}
\label{sec:cappgappkapp}
The prototype mentioned in the previous section resulted in three separate applications named CAPP, GAPP and KAPP. These are described in an overview below.  

\subsection{GAPP}
GAPP is an Android application targeted towards the parents or guardians of the children. 
Its basic functionality is to view logs on how often a child needs medication, how the child has been feeling the last couple of days, according to the asthma traffic light system, and to set up alarms for the child. 
CAPP and GAPP work together as a pair, so a child may only have one parent and vice versa. %Er siste setning nødvendig?


\subsection{CAPP}
CAPP is an Android application targeted towards the children. It launches the alarms given by parents and guides children during their medication. After the medication is administred, the child gets a gold star in his/her treasure chest.    

%PICTURES, OR IT DIDN'T HAPPEN!


\subsection{KAPP}
KAPP is another application targeted towards children. The application runs on a Karotz\cite{karotz}, which is a small robot bunny \ref{fig:karotz}. The purpose of the Karotz is to reminder the children when it is time to take their asthma medicine and give instructions during treatment. In order to interact with the Karotz, children may use either a Nanoz (a small bunny with an integrated RFID) or by pressing a button on the top of the Karotz' head.    



\subsection{Known areas for improvement}
\label{sec:improvements}
As Aaberg, Aarseth, Dale, Gisvold and Svalestuen finished their work, they commented on several areas of potential improvement for CAPP/GAPP/KAPP. This document is reprinted in its entirety in Appendix \ref{app:furtherWork} (after permission from Aaberg, Aarseth, Dale, Gisvold and Svalestuen). The main topics for improvement were
\begin{enumerate}
\item{Reward System}
\item{Distraction sequence for children}
\item{Web application}
\item{Support for more children}
\end{enumerate}

These comments are used as a basis when we decide what to improve in this project. 
%In addition, we have discovered a potential in sending out emails with records, which perhaps will go directly to the child's doctor. Hvor skal vi skrive om dette? 


\input{Chapters/Chapter2/existingproducts.tex}

\input{Chapters/Chapter2/existingresearch.tex}
