\textbf{PHd in Psychology. Expertise on reward systems when raising a child.} 

\textbf{Date: 25th of March}

\textbf{Place: Trondheim}

\emph{How do children react to reward systems such as the one in AsthmAPP?}

Children react very differently regarding reward systems. Some children find the rewards interesting, while some may not care at all. A common problem is that they may not be able to see the value of a reward given in the future. Younger children tend to choose rewards given immediately instead of a bigger reward given in the future\cite{mischel1972cognitive}.
The difference in how children percieve the value of a reward is very individual and there may be huge differences between age groups. 


\emph{Is there a possibility that children may manipulate the reward system by pretending to be sicker than they are?}

It is difficult to determine if there is a risk of children pretending to be sick. Children often do not like going to the doctor's office, which may stop them from pretending to be sick.


\emph{The parents set the rewards themselves, how do you think this will work?}

The rewards has to be interesting for the individual child, and must be tailored to their interests. 

\emph{Do you think the reward system can lead to jealousy between children?}

Children percieve rewards differently, and a reward for one child may not be interesting for the other child. However if one child gets a reward that is much more valuable than the other children, if may lead to a situation where the children who recieve lesser rewards may be jealous. The parents of the children in the same class/kindergarten can make an agreement on what rewards should be set, in order to give equal rewards. It is important to find a reasonable level for the value of the rewards, to ensure it will not be a burden to the parents.

Rewards do not have to be a material reward, it may be a fun activity or letting the children choose what they will eat for dinner. Doing something entertaining with their parents can be as much of a rewards as a physical toy. An example of an easy and fun reward is to eat dinner sitting underneath the table or taking a walk in the woods. It is important for you [the developers] to tell the parents that the reward does not need to be material, but can be simple and easy rewards.


\emph{Can the reward system lead to differences between children that use the application and recieve rewards and children that do not use the application?} 

There at not that many children with asthma in each kindergarten. I believe that parents will talk to each other and share experiences which may result in positive sharing of knowledge. 


\emph{The stars earned in the application are not removed. Will this cause a problem with regarding teaching children the value of money and rewards?}

This is different from one child to another. Some children are ``collectors'' and would not spend the stars if they go away, but instead hoard them. There will be a risk that these children never spend their stars on rewards if they have to remove stars to get rewards.

\textbf{[Demonstration of how AsthmAPP works]}

Have you [the developers] thought about letting the players play a game as a reward? Games such as Flappy Bird \fnurl{Flappy Bird}{http://flappybird.io/} are very popular with children, and a round doesn't take such a long time. 


It is also important to remember that the reward must be reflected in the severity of the task. 

\textbf{[Demonstration of AsthmaBuddy]}

I believe that a cute bear like this may help in making children more positive to remembering their medicine. For a small child the bear itself may be enough of a reward.


\emph{The use of AsthmAPP and AsthmaBuddy are quite repetitive over time. Do you think it can be boring over time?}

A treatment takes less than 2 minutes, which will help. The app should have support for experts children, so they do not have to follow the instructions when they have become expert users. 

I do not see any negative aspects with the system. Leaving the reward system for the parents to choose is a good solution, but will require advice and information in order for it to work as a positive manner for both parents and children. 
You must also remember that it must not take a long time between the activity and the rewards, since children may not see the connection.

