\chapter{Usability}
\label{Usability}

This chapter will give a brief definition of what usability is, and how user tests can help us improve it. Since are applications are targeted towards both children and adults, we will give a description of how the usability tests for these gorups will differ. We will also explain how the user testing is performed at \ldots

\section{What is usability?}
There are many ways to describe usability. 

The International Organization for Standardization(ISO) has a definition of the term usability [insert reference from bibliography]: 

Extent to which a system, product or service can be used by specified
users to achieve specified goals with e↵ectiveness, efficiency
and satisfaction in a specified context of use.

The same document defines the context of use as:

Users, tasks, equipment (hardware, software and materials), and
the physical and social environments in which a product is used.

These definitions covers how the system is used, the user's thoughts about the use and the context of the system. This can be broken further down into several subgoals in order to achieve better usability, and to give us a better insight on what usability is. 
These subgoals are:

\begin{enumerate}
\item{How precise is the user able to perform a task using the application?}
\item{How much resources(for example time, or number of tries) was used to perform the given task using the application?}
\item{How many errors occurred?}
\item{Did the user find the use satisfactory?}

User-centered design is a way of designing with the user in mind. By using this technique these goals are achieveable. User-centered design is about getting feedback from the users during the design and development process. Always thinking about how the user would solve this problem, and consolidate the users when in doubt is a fundamental part of user-centered design. The user's opinion is the measure of how good the system performs and the user's feedback defines how you score on usability. [Should have reference]

\section{How to test usability}
There are many ways to create a good user experience. Having knowledge of expert opinions is always a good idea, and using user-centered design techniques are also a wise way to go. 

\section{How to test usability on children and toddlers}