\chapter{Interview Questions}
\label{app:interviewquestions}


We conducted our interviews as semi-structured interviews. In order to achieve a creative process, we prepared some topics for discussion. If the interview object came up with interesting feedback or answers, we elaborated on his/her answers


\paragraph{Gamification}
When discussing gamification we had the following topics:

\begin{enumerate}
	\item{What types of gamification do you know? And where have these been used?}
	\item{Can you think of possible gamification concepts that can be used with the treatment of asthma?}
	\item{Can you think of rewards for the gamification concept?}
	\item{Can you think of find any positive measures gamfication may bring?}
	\item{Can you think of any negative measures or risks with the usage of gamification?}
\end{enumerate}


\paragraph{Tangible User Interfaces}
When discussing tangible user interfaces we had the following topics:

\begin{enumerate}
	\item{Have you used any tangible user interfaces before?}
	\item{What do you think of the having a tangible user interface as a help tool in your home?}
	\item{Should the tangible user interface be portable or stationary?}
	\item{What functions do you think the tangible user interface system should have?}
\end{enumerate}


\paragraph{Demonstration of AsthmaBuddy}
We demoed AsthmaBuddy for the user, in order for them to understand what we are working with and how to operate AsthmaBuddy. We then discussed some topics:

\begin{enumerate}
	\item{Do you have any ideas for improvement?}
	\item{Regarding the ideas mentioned earlier, can you think of any way to integrate them with the system?}
	\item{The application requires that you manage rewards yourself, what do you think of this?}
	\item{Can you think of other functions the bear could have?}
	\item{What do you think of support for information about pollen forecast and air quality?}
	\item{Should the bear me more active that it is now?}
	\item{Should the bear have more support for showing information?}
	\item{Should the system have support for sending reports to the doctor about medication plans and treatments finished?}
	\item{What other interaction methods should be integrated?}
\end{enumerate}


\subsection{Interviews with asthma experts}

We conducted interviews with medical personel with expertise on asthma