\section{Existing Research}
\label{sec:existing-research}

This section will give a foundation on some of the research performed on using technology in combination with diseases and children. 


\subsection{Monitoring Asthma with Mobile Technology}
Research on self-management of monitoring one's asthma condition has already been carried out. Much of this research was carried out by using SMS (Short Messaging System) technology. In 2009, Andh\o j  et. al.\cite{anhoj2004feasibility} did a feasability study to check how users would respond to a SMS-reminder. Their methodology was to send SMS a couple of times a day, and have the users respond to their peak flow and answer yes/no questions. Users could then access a web page to see different statistics on peak flows, how they've felt the last couple of days, etc.

Andh\o j \etal{} concluded that SMS is a feasible solution for collecting asthma diary data, mainly because the SMS technology was an important part of the participants' everyday life. Although SMS is a great technology to be used for this purpose, few children in our target group are old enough to use this technology. According to \emph{Senter for IKT i utdanningen} (Center for ICT in education), about 40\% of Norwegian children below the age of 3 years old have used a tablet, and 6 out of 10 children below the age of 6 have used a touch screen device\cite{nrkchilduse}. Thus our target group is likely to be familiar with the technology we plan to use.  


\subsection{Children and Mobile Devices}
In 2013, \url{www.babies.co.uk} posted results of a poll they had posted on how many toddlers are using smartphones or tablets each day\cite{babiesusageoftablets}. Over 1000 participants responded,  and according to the survey, 14\% of the responders allowed their children to use smartphones or tablets more than 4 hours a day. Considering the normal awake time of a small child, the children spent a considerable amount of their day playing with a smartphone. With this in mind, we aim to make an application that is used for a short period of time with each use. AsthmAPP and AsthmaBuddy will be tools for helping the children, not a toy or a game.


\subsection{Children and Gestures}
\label{sec:childrenandgestures}
Abdul Aziz et. al.\cite{aziz2013children} performed a study on which gestures children are able to comprehend when playing with an iPad. They tested children's ability to gesticulate on a variety of applications suited for children. The children were between the age of 2 - 12, three children in each age group. The study showed the following restrictions:

\begin{itemize}
  \item 2 year olds have difficulties with pinching and are unable to drag and drop, spread and rotation of the device, and are not able to focus on the application. 
  \item 3 year olds have difficulties with drag and drop until they are told to do so, in addition to having problems with pinch and spread. 
  \item 4 year olds have difficulties with drag and drop. 
\end{itemize}
Children at the age of five and above are able to do all the normal gestures at a tablet. As CAPP is currently only available for mobile devices, this is a cause for concern. The main issues to notice is pinching and drag and drop. An iPad is fairly large compared to the size of the child's hand. There is reason to believe that gestures may be more difficult on smaller screens, however, we were unable to find research to support this presumption. In order to make AsthmAPP as child friendly as possible, it only uses ``swiping'' gestures and button presses for navigation.

\subsection{Assessment of Existing Asthma Applications}
In 2012, Huckvale et. al.\cite{huckvale2012apps} conducted an assesment on the existing asthma-related applications on both Google Play\fnurl{Google Play}{http://play.google.com} and App Store\fnurl{Apple App Store}{http://www.apple.com/itunes/features}. They assessed 103 different apps with english as the native language. Out of these applications, 


\emph{``No apps for people with asthma combined reliable, comprehensive information about the condition with supportive tools for self­management''}\cite{huckvale2012apps}. 


They concluded that doctors should be careful when recommending apps for patients with the purpose of self management of asthma.