\chapter{Discussion and Conclusions}
\label{chp:masterconclusion}

This chapter discusses some of the main discoveries of our project. The chapter concludes by presenting the research questions, providing answers where possible, and evaluating the process of obtaining these answers. 

\section{Discussion}
\label{sec:discussion}


\input{Chapters/masterconclusion/discussion.tex}

\section{Process Evaluation}
\label{sec:processevaluation}
As with all other software development projects, the development of AsthmAPP and AsthmaBuddy has hit some bumps in the road. This chapter will look into possible improvements of the developments process. Second it will evaluate the experiment design and point out different elements which could have been done differently.

\subsection{Difficulty Finding Test Users}
\label{sec:difficultyfindingtestusers}
When performing user tests and interviews involving gathering personal medical information, there are requirements to be followed. Before contacting potential test users, the research project must be evaluated by an ethical committee\fnurl{Regional Etisk Komite}{https://helseforskning.etikkom.no/ikbViewer/page/forside?\_ikbLanguageCode=n}, and while the paperwork have easy-to-follow standards, this took some time\footnote{Our project was authorized in January 2014, under case number REK 2012/159}. 

The search for potential test users proved more difficult than initially anticipated. We contacted different hospitals and persons with expertise on asthma. We asked them to help us recruit test persons for our project. In order for the hospitals to help us, we needed an approval from their marketing/ethical committee. In our efforts we were a bit unlucky. After applying for an approval, we did not hear from the hospital in a while. After numerous phone calls and e-mails, we got the answer that the person responsible for our processing our application had been on sick leave for a long period of time. In hindsight we understand that this process should have started some months before the actual project, in order to allow for such unforeseen events. 

In parallell to the contact with hospitals and doctors we tried recruiting test persons through friends, colleagues, social media and mailing lists from NTNU and local organizations. This proved less fruitful than we hoped. We have no concrete feedback as to why we had so little response, but we have our assumptions. Firstly, the user group is a very specific group. There might not be that many children living in Trondheim at the age of 3 - 7 years, suffering from asthma, who also have parents willing to participate in our research. Secondly, people tend to not care if they do not get an attractive reward for helping, and since we had little to offer in terms of economical compensation or rewards, the interest might have withered away for some people. Thirdly, there may have been scepticism from the potential test users. While all the different paperwork was in order and the project may prove positive for the children and parents within the target group, the fact that we are two students writing a master thesis may be less encouraging\footnote{We \emph{believe} that if the researchers were publicly acknowledged, it would have been a bit easier to recruit users}.


\subsection{Co-Design Sessions}
\label{sec:codesignsessionsdifficulties}
Our original plan was to arrange co-design sessions with several experts present at the same time. We believe this would have helped the creativity of the feedback for \app{} and \ab{}. However, this proved too difficult to arrange. The persons we wanted to invite were very busy and after several failed attempts to find a time suitable for all experts, we gave up trying to arrange co-design sessions. The arguments stated Section \ref{sec:receptionofrewardsystem} is an example of a situation where a focus group session might have lead to an interesting discussion, since the interview subjects did not completely agree on the differentiation of rewards based on health state.

  
\section{Conclusions}
\label{conlusions}

The study was set out to explore the concept of gamification and tangible user interfaces in the treatment of asthmatic children.

The research questions presented in Chapter \ref{sec:researchquestions} provides a basis for summarization of results discussed in Chapter \ref{chp:results}. 

\textbf{RQ1: How can gamification be used for motivating children to take their asthma medicine?}

During our research, we have looked into several methods for how to apply gamification to these treatments. 

Based on the information gathered through privacy laws, user tests, literature study and interviews, we have developed a prototype containing a subset of these mechanisms. As discussed in Section \ref{sec:bartlesfourplayertypes}, we identified mirroring user behavior, experience points, real-world rewards and avatar systems as suitable for this domain. We have developed a prototype, \app{}, which makes use of experience points, real-world awards and mirroring user behavior, in order to motivate children to take their medicine. The prototype was validation tested with three asthmatic children, which provided non-conclusive, but positive results.

In a broader context, we believe gamification can be applied to the treatment of children suffering from a wide range of diseases. Further research for how to tailor gamification to specific diseases should be conducted.  

\textbf{RQ2: How can tangible user interfaces be used to help children with asthma?}

Understanding the effect asthma has on the child is central to treating the disease. Many families find the treatment process troublesome, and sometimes apply treatments incorrectly, at the wrong time, or even forget to perform the treatment. This study has researched different ways tangible user interfaces can be used to relieve parents of this responsibility. 
We have identified three key areas where tangible user interfaces may be applied to the treatment of asthmatic children. These areas are \emph{learning}, \emph{motivating} and \emph{distracting}. 

We developed a prototype, \ab{}, which is capable of reminding children to take their medicine, guiding them through the process and rewarding them afterwards. Although \ab{} in its current state did not incorporate all of the aspects identified, it is a starting point for further research in this context.   

As a stand-alone system, it is hard to see a future for \ab{} without any connections to other systems (such as a smartphone application). We have relied heavily on the ability to synchronize user data with \app{}, in order for \ab{} to be aware of alarms, rewards and treatment plans. Due to the amount of information necessary in the treatment of asthmatic children, it would be difficult to display all of it on a tangible user interface such as ours in a non-obtrusive manner.  


\section{Validity of our Results}
\label{sec:validity}

\textbf{Sample size}

The validity of our study suffers from a low sample size of test users. Testing \ab{} and \app{} on three children and two adults are not enough to draw any conclusions of whether or not \app{} and \ab{} has potential to become a successful tool or not. As such, we have included testing on several more children in Chapter \ref{chp:futurework} - Further Work.    

\textbf{Interview transcripts}

Interviews were performed by having one interviewer and one transcriber, with no means of recording. In hindsight, we should have recorded the interviews in order to process them more in depth, in addition to making it easier to ask follow-up questions at a later stage in the project. The interviews were performed in Norwegian, and later translated to English by us. The transcripts were then sent to our interview subjects for validation of citations. Even though the transcripts were validated by the interview subjects, some of the semantics could have been lost during the translation. 


\textbf{Testing environment and equipment}

The testing lab at NSEP has little similiarities to a home, where the user will normally use \ab{} or \app{}. The lab is situated within a hospital building, which again is next door to the child clinic of the hospital. This may have intimidated our users and placed them in a situation they were not comfortable with. 

During the user tests we used placebo medicine, which contains compressed air instead of medication. The users were told this very clearly before the test started. Since users of asthma medicine is adviced to not overdose on medication, this was important to tell the users. Even though the users were told very clearly that the medicine had no effect, one of the users did not want to take the medicine, and asked if it was okay if the container was not pressed, so the particles were not released into the breathing chamber. 
We also used masks that we brought with us. The fact that the masks differed from the masks the users have at home may have made them insecure or intimidated. This may have biased the outcome of the user test. 


\textbf{Time period}

A central aspect to gamification is whether it will work over a longer period of time. While we have discussed \app{}'s gamification system and how it makes it own spin on gamification by being so user-centric, we have not researched how the user reacts over time. Preferrably we would have done user testing over a period of time, in order to receive continuous feedback on how the children and their parents reacted to using the gamification system over a week, a month, or several months. 

The lack of testing over a longer period of time is a threat to the conclusions regarding the use of gamification. 

